%!TEX root = ../dissertation.tex
It is difficult to properly convey my deep sense of gratitude to the many
wonderful people who have helped and enriched my life during my stay at UW. Suffice it to say I must be very blessed.

I consider myself very lucky to have Prof. Ben Recht as my advisor. He has a
boundless enthusiasm for research and is a constant source of inspiration and
energy. I would like to thank him for his excellent academic mentoring and his
readiness to help with any problem. Without his pragmatism and brilliance, I
doubt I would have spent my time fruitfully and I am grateful to him for setting
a great example. He has fostered a unique collaborative atmosphere and I will
cherish my stay at the wonderful Wisconsin Institute of Discovery (WID) for a
long time to come.

The work I present in the thesis arose from a collaboration with Prof. Ben Recht
and postdoctoral students Dr. Gongguo Tang and Dr. Parikshit Shah. I will
definitely remember the many wonderful discussions I have had with them and
their comradeship, and I wish them a wonderful future. My peers Gautam, Matt,
Sumeet, Kevin, Aniruddha, Okan, Krishna, Victor, Charles, Nikhil and Zach made
my stay at WID very enjoyable. I would also like to thank Laura, Aarti, Raman
and Waheed for their friendship and their invaluable help during difficult
times.

I would like to thank my committee for their support and guidance throughout.
Prof. Barry Van Veen taught a very entertaining course which piqued my interest
in Estimation Theory and I would like to thank him for his unique linear algebra
perspective of it. Thanks to Prof. Nowak for engaging me with thoughtful
discussions, offering excellent research courses, and especially also for
building a wonderful team of students I've had the fortune of interacting with.
I always felt very comfortable stopping by Prof. Steve Wright's office when I
have a question and I did so numerous times knowing that I can get a precise and
quick answer. Thank you for sharing your expertise.

I took numerous courses taught by Prof. John Gubner and have always thoroughly
enjoyed his wonderfully precise lectures. I admire his patience and readiness to
provide a thorough answer to questions and would like to especially thank him
for teaching me to be rigorous and meticulous. I owe Prof. Gubner many thanks
for providing excellent advice, support, encouragement and giving me the gift of
his time. I also feel especially indebted to Prof. Amir Assadi, Prof. Brian
Gould and Prof. Ross Barmish for their encouragement, support and advice.

I could not have done anything without the unwavering faith my family has had in
me. Thank you Amma, Appa and Karoo for believing in me and supporting me
throughout. Last, but not the least, I have much to thank my wife for, who had
to endure the several ups and downs of my life. Thank you for your unconditional
love, your many selfless sacrifices, advice, encouragement and trust. 
